\TITLE

### 2020-12-18 vonLaszewski-covid.tex
add row color

\begin{table}[!p]
\caption{Best models for each risk factor and their respective
  errors. The model that uses no risk factor is highlighted in grey.}
\label{tab:top-1}
\bigskip
\centering
%\resizebox{1.0\textwidth}{!}{ 
\begin{tabular}{rrrrrlrl}
\toprule
 \makecell{Place/\\Rank} & 
\makecell{Risk Factor} &  
\makecell{RMSE\\Cases} &  
 \makecell{RMSE\\Death} &  
 \makecell[r]{Cumu-\\lative \\Error \\Cases} &  
 \makecell[r]{Cumu-\\lative \\Error \\Death} &  
 \makecell[r]{Number of \\Days as \\Input} \\
\midrule
1 & POP\_DENSITY\_2010 & 0.055443 & 0.067617 & 7.94 & 22.74 & 5 \\
2 & PHLTH & 0.054795 & 0.068529 & 8.01 & 20.55 & 3 \\
3 & INSURANCE & 0.055199 & 0.067641 & 8.07 & 20.43 & 4 \\
4 & PERCENTBLACKS & 0.055028 & 0.067207 & 8.12 & 20.17 & 4 \\
5 & PERCENTHISPANICS & 0.056061 & 0.067489 & 8.22 & 19.04 & 5 \\
6 & NHOSP & 0.054621 & 0.068255 & 8.26 & 20.10 & 3 \\
7 & INSURANCE & 0.054557 & 0.068572 & 8.34 & 24.61 & 3 \\
8 & CHOLSCREEN & 0.054712 & 0.069121 & 8.37 & 21.70 & 3 \\
9 & DIABETES & 0.054586 & 0.067636 & 8.40 & 20.50 & 5 \\
10 & STROKE & 0.054160 & 0.066906 & 8.45 & 20.16 & 4 \\
11 & CHD & 0.054027 & 0.067642 & 8.46 & 21.93 & 5 \\
12 & CHECKUP & 0.054927 & 0.067652 & 8.51 & 20.42 & 5 \\
13 & NBEDS & 0.054146 & 0.067536 & 8.54 & 21.15 & 5 \\
14 & SVI\_OVERALL & 0.054795 & 0.067676 & 8.58 & 19.94 & 5 \\
15 & KIDNEY & 0.054600 & 0.067565 & 8.61 & 21.86 & 5 \\
16 & CASTHMA & 0.055089 & 0.068248 & 8.63 & 22.58 & 5 \\
17 & BLACK & 0.054547 & 0.068266 & 8.68 & 20.49 & 3 \\
18 & BPMED & 0.054685 & 0.068920 & 8.74 & 21.69 & 3 \\
19 & LPA & 0.054323 & 0.067149 & 8.75 & 19.54 & 5 \\
20 & CSMOKING & 0.053716 & 0.066898 & 8.75 & 19.01 & 5 \\
21 & ARTHRITIS & 0.054053 & 0.068716 & 8.83 & 20.94 & 3 \\
22 & POVERTY & 0.055029 & 0.068672 & 8.84 & 22.02 & 3 \\
23 & ESTBEDS & 0.054545 & 0.067267 & 8.86 & 21.22 & 4 \\
24 & MHLTH & 0.054864 & 0.068742 & 8.90 & 19.53 & 3 \\
25 & SENIOR & 0.055079 & 0.069024 & 8.93 & 21.23 & 3 \\
26 & COPD & 0.055589 & 0.068250 & 8.93 & 23.26 & 4 \\
27 & CANCER & 0.054500 & 0.068363 & 8.99 & 19.70 & 3 \\
28 & NBEDS/1000 & 0.054397 & 0.068491 & 9.05 & 21.89 & 3 \\
29 & BPHIGH & 0.054609 & 0.067346 & 9.13 & 21.29 & 4 \\
30 & NONE &\rowcolor{black!5} 0.054868 & 0.069432 & 9.26 & 25.88 & 3 \\
31 & HIGHCHOL & 0.056429 & 0.069345 & 9.28 & 20.98 & 3 \\
32 & BINGE & 0.054317 & 0.067638 & 9.32 & 21.00 & 5 \\
33 & OBESITY & 0.054469 & 0.068540 & 9.50 & 20.65 & 3 \\
34 & SVI\_MINORITY & 0.055094 & 0.067443 & 9.54 & 21.53 & 4 \\
\bottomrule
\end{tabular}
%}
\end{table}

>>>>

\begin{table}[!p]
\caption{Best models for each risk factor and their respective
  errors. The model that uses no risk factor is highlighted in grey.}
\label{tab:top-1}
\bigskip
\centering
%\resizebox{1.0\textwidth}{!}{ 
\begin{tabular}{rrrrrlrl}
\toprule
 \makecell{Place/\\Rank} & 
\makecell{Risk Factor} &  
\makecell{RMSE\\Cases} &  
 \makecell{RMSE\\Death} &  
 \makecell[r]{Cumu-\\lative \\Error \\Cases} &  
 \makecell[r]{Cumu-\\lative \\Error \\Death} &  
 \makecell[r]{Number of \\Days as \\Input} \\
\midrule
1 & POP\_DENSITY\_2010 & 0.055443 & 0.067617 & 7.94 & 22.74 & 5 \\
2 & PHLTH & 0.054795 & 0.068529 & 8.01 & 20.55 & 3 \\
3 & INSURANCE & 0.055199 & 0.067641 & 8.07 & 20.43 & 4 \\
4 & PERCENTBLACKS & 0.055028 & 0.067207 & 8.12 & 20.17 & 4 \\
5 & PERCENTHISPANICS & 0.056061 & 0.067489 & 8.22 & 19.04 & 5 \\
6 & NHOSP & 0.054621 & 0.068255 & 8.26 & 20.10 & 3 \\
7 & INSURANCE & 0.054557 & 0.068572 & 8.34 & 24.61 & 3 \\
8 & CHOLSCREEN & 0.054712 & 0.069121 & 8.37 & 21.70 & 3 \\
9 & DIABETES & 0.054586 & 0.067636 & 8.40 & 20.50 & 5 \\
10 & STROKE & 0.054160 & 0.066906 & 8.45 & 20.16 & 4 \\
11 & CHD & 0.054027 & 0.067642 & 8.46 & 21.93 & 5 \\
12 & CHECKUP & 0.054927 & 0.067652 & 8.51 & 20.42 & 5 \\
13 & NBEDS & 0.054146 & 0.067536 & 8.54 & 21.15 & 5 \\
14 & SVI\_OVERALL & 0.054795 & 0.067676 & 8.58 & 19.94 & 5 \\
15 & KIDNEY & 0.054600 & 0.067565 & 8.61 & 21.86 & 5 \\
16 & CASTHMA & 0.055089 & 0.068248 & 8.63 & 22.58 & 5 \\
17 & BLACK & 0.054547 & 0.068266 & 8.68 & 20.49 & 3 \\
18 & BPMED & 0.054685 & 0.068920 & 8.74 & 21.69 & 3 \\
19 & LPA & 0.054323 & 0.067149 & 8.75 & 19.54 & 5 \\
20 & CSMOKING & 0.053716 & 0.066898 & 8.75 & 19.01 & 5 \\
21 & ARTHRITIS & 0.054053 & 0.068716 & 8.83 & 20.94 & 3 \\
22 & POVERTY & 0.055029 & 0.068672 & 8.84 & 22.02 & 3 \\
23 & ESTBEDS & 0.054545 & 0.067267 & 8.86 & 21.22 & 4 \\
24 & MHLTH & 0.054864 & 0.068742 & 8.90 & 19.53 & 3 \\
25 & SENIOR & 0.055079 & 0.069024 & 8.93 & 21.23 & 3 \\
26 & COPD & 0.055589 & 0.068250 & 8.93 & 23.26 & 4 \\
27 & CANCER & 0.054500 & 0.068363 & 8.99 & 19.70 & 3 \\
28 & NBEDS/1000 & 0.054397 & 0.068491 & 9.05 & 21.89 & 3 \\
29 & BPHIGH & 0.054609 & 0.067346 & 9.13 & 21.29 & 4 \\
\rowcolor{black!5} 30 & NONE & 0.054868 & 0.069432 & 9.26 & 25.88 & 3 \\
31 & HIGHCHOL & 0.056429 & 0.069345 & 9.28 & 20.98 & 3 \\
32 & BINGE & 0.054317 & 0.067638 & 9.32 & 21.00 & 5 \\
33 & OBESITY & 0.054469 & 0.068540 & 9.50 & 20.65 & 3 \\
34 & SVI\_MINORITY & 0.055094 & 0.067443 & 9.54 & 21.53 & 4 \\
\bottomrule
\end{tabular}
%}
\end{table}
